Spatial variation of the native colon microbiota in healthy adults

### 2018-01-27 submission/manuscript_with_revisions.Rmd
updated manuscript

### Figures

@@

![Fig 1](../submission/fig1.jpg)

@@

![Fig 2](../submission/figure_2.pdf)

@@

![Fig 3](../submission/figure_3.pdf)

@@

![Fig 4](../submission/figure_4.pdf)

\newpage
####Figure 5
Taxa specific to the distal and proximal sides of the colon. Top five OTUs that are most important for the classification model for the distal mucosa and lumen (A) and the proximal mucosa and lumen (B). The vertical lines represent the median values for each OTU.

![Fig 5](../submission/figure_5.pdf)

@@

![Fig 6](../submission/figure_6.pdf)

####Figure S1
Location and relative abundance of cancer-associated OTUs. Relative abundance was calculated and plotted by sample site for each OTU of interest: (A) _Fusobacterium nucleatum subsp. animalis_ (B) _Fusobacterium varium_ and (C) _Porphyromonas asacharolytica_ 
![Fig S1](../submission/figure_S1.pdf)

>>>>

### Figure legends

@@

@@

@@

@@

####Figure 5
Taxa specific to the distal and proximal sides of the colon. Top five OTUs that are most important for the classification model for the distal mucosa and lumen (A) and the proximal mucosa and lumen (B). The vertical lines represent the median values for each OTU.

@@

####Figure S1
Location and relative abundance of cancer-associated OTUs. Relative abundance was calculated and plotted by sample site for each OTU of interest: (A) _Fusobacterium nucleatum subsp. animalis_ (B) _Fusobacterium varium_ and (C) _Porphyromonas asacharolytica_
